---
title: "Assignment 9"
author: "Backman"
date: "4/23/2020"
output: html_document
---
<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
}
</style>

<style>
div.gray { background-color:#7e8687; border-radius: 5px; padding: 20px;}
</style>
<div class = "gray">



<style>
div.blue { background-color:#9dc9d1; border-radius: 5px; padding: 20px;}
</style>
<div class = "blue">

## **Instructions:**
#### **All file paths should be relative, starting from the Assignment_9 directory!! (where you found this file)**

#### **This means that you need to create a new R-Project named "Assignment_9.Rproj" in your Assignment_9 directory, and work from scripts within that.**


### **For credit...**

#### 1.  Push a completed version of your Rproj and R-markdown file (details at end of this assignment) to GitHub
#### 2.  Your score will also depend on your analyses and presentation of your final report

____________

### Your tasks:

+ Use the data set "../../Data/GradSchool_Admissions.csv"
+ You will explore and model the predictors of graduate school admission
  - the "admit" column is coded as 1=success and 0=failure
  - the other columns are the GRE score, the GPA, and the rank of the undergraduate institution, where I is "top-tier."
+ Document your data explorations, figures, and conclusions in a reproducible R-markdown report
+ Upload your **self-contained** R project, including knitted report, to GitHub in *your* Assignment_9 directory

#### **Load Libraries**
```{r, message=FALSE}
library(tidyverse)
library(modelr)
library(GGally)
library(lindia)
library(skimr)
library(patchwork)
library(caret)
```

#### **Load data**
```{r, message=FALSE}
df <- read_csv("./GradSchool_Admissions.csv")
```

#### **Explore data**
```{r}
summary(df)
df %>% ggpairs()
```

#### **Clean data**
```{r}
df$rank <- factor(df$rank)
df$admit <- as.logical(df$admit)
```

#### **Making models**
```{r}
mod1 <- glm(formula = admit ~ gre + gpa + rank, data = df, family = "binomial")
mod2 <- glm(formula = admit ~ gre * gpa * rank, data = df, family = "binomial")
```

### **Comparing models: best fit line**
```{r}
mod1mse <- mean(residuals(mod1)^2)
mod2mse <- mean(residuals(mod2)^2)

mod1mse ; mod2mse
```
#### The lowest number shows the best fit line model.  mod2mse has the best fit line, so we will use that model.

### **Evaluating predictions**
```{r, message=FALSE}
df_mod2 <- add_predictions(df, mod2, type = "response") 
allmods <- gather_predictions(df, mod1, mod2) 
head(allmods)
```

### **Compare allmods to visually see best model**
```{r}
ggplot(allmods,aes(x=gpa,col=rank)) +
  geom_point(aes(y=pred)) +
  geom_smooth(method = "lm", aes(y=pred)) +
  facet_wrap(~model) +
  theme_bw()
```

#### Both models seem to follow the trend, but since the line of best fit was better for mod2, we will use mod2. 

### **Look at predictions for model 2**
```{r, message=FALSE}
p1 <- ggplot(df_mod2, aes(x=gpa, y=pred, color=admit)) + theme_minimal() +
  geom_point() + geom_smooth(method = "lm")
p1

p2 <- ggplot(df_mod2, aes(x=gre, y=pred, color=admit)) + theme_minimal()  +
  geom_point() + geom_smooth(method = "lm")
p2 
```

#### Both gre and gpa seem to be good indicators of whether you will be admitted or not.  

```{r, message=FALSE}
p3 <- ggplot(df_mod2, aes(x=gpa, y=pred, color=rank)) + theme_minimal() +
  geom_point() + geom_smooth(method = "lm")
p3

p4 <- ggplot(df_mod2, aes(x=gre, y=pred, color=rank)) + theme_minimal()  +
  geom_point() + geom_smooth(method = "lm")
p4
```
Looks like both gre and gpa are good indicators of the school rank that you are admitted into.  

Based off of these graphs, it looks like gpa and gre contribute whether you will be admitted into a school.  The higher the gre and gpa, the more likely you are to get into a higher ranking school.

